
Rental property group booking is an activity that often involves multiple stakeholders and spans multiple days. Existing property search tools like Airbnb enable users to look for properties based on many criteria but lack explicit support for collaborative search. Furthermore, these tools tend to stop at search, failing to incorporate ways to mediate agreement within their systems. We present \tool, a collaborative real estate search tool designed to empower groups of remote users to search for and agree on a rental property asynchronously. With \tool, we embark on a systematic design process, where we first articulate the tasks involved and the challenges faced in our application. Then, we utilize design principles motivated by the literature to create a tool that aims to maximize group satisfaction with the selected property. This process led to the design and implementation of UI features that aid search, group communication and agreement, including a mediating bot, a contract creation and signing component, and templates for the specification of house rules that help group members set terms for co-living and for negotiating monetary and non-monetary contributions to a group rental. Through a user study, we evaluate how users interacted with and without \tool's unique features in a group booking exercise. We describe the differences in the observed interactions and explain how effective the different features aid the group search and agreement process. We also report the qualitative experiences of the groups with \tool.